Forcing for Isabelle

### 2018-12-21 LICS/recursion.tex
Hablando un poco de check

\fbox{Creo que deberíamos poner acá \isa{check} y \isa{check\_in\_M} }

>>>>

We close our discussion of names and their values by making explicit
the names for elements in $M$, once more we refer to
\cite{2018arXiv180705174G} for our formalization. The definition of
$\chk(x)$ is a straightforward $\in$-recursion:
\begin{equation*}
  \label{eq:def-check}
  \chk(x)\defi\{\lb\chk(y),\1\rb : y\in x\}
\end{equation*}
It can be easily proved by $\in$-induction that $\val(G,\chk(x))=x$.
To conclude $M\subseteq M[G]$ one also needs to have $\chk(x) \in M$;
this result requires the internalization of recursively defined
functions. We indicate explicitly where we use this assumption.
